---
title: "RWorksheet#5_group(freires,rocillo,sanico)"
output: pdf_document
date: "2024-11-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Extracting TV Shows Reviews

1. Each group needs to extract the top 50 tv shows in Imdb.com. It will include the rank, the title of the
tv show, tv rating, the number of people who voted, the number of episodes, the year it was released.
It will also include the number of user reviews and the number of critic reviews, as well as the popularity
rating for each tv shows.

```{r}
library(polite)
library(rvest) 

url <- "https://www.imdb.com/chart/toptv/?ref_=nv_tvv_250"

session <- bow(url,
               user_agent = "top 50 tv shows")
session
session_page <- scrape(session)

div_elements <- html_nodes(session_page,'div.sg-col-4-of-24.sg-col-4-of-12.s-result-item.s-asin.sg-col-4-of-16.sg-col.s-widget-spacing-small.sg-col-4-of-20')


<meta name="viewport" content="width=device-width">
```

```{r}
ranks <- character()
title <- character()
tv_rating <- character()
num_of_people_voted <- character()
num_of_episodes <- character()
year_it_was_realeased <- character()

num_of_user_reviews <- character()
num_of_critic_reviews <- character()
popularity <- character()
rating_for_each_tv_shows <- character()

```

```{r}
year_it_was_realeased <_ "sc-5bc66c50-5 hVarDB cli-title-metadata" class="sc-5bc66c50-6 OOdsw cli-title-metadata-item">2008–2013</span><span class="sc-5bc66c50-6 OOdsw cli-title-metadata-item">62 eps</span><span class="sc-5bc66c50-6 OOdsw cli-title-metadata-item">TV-MA</span></div>

```





2. From the 50 tv shows, select at least 5 tv shows to scrape 20 user reviews that will include the reviewer’s
name, date of reviewed, user rating, title of the review, the numbers for “is helpful” and “is not helpful”,
and text reviews.

```{r}
```

3. Create a time series graph for the tv shows released by year. Which year has the most number of tv
shows released?

```{r}
```

Extracting Amazon Product Reviews

#sunscreen
```{r}

library(rvest)
library(polite)

url <- “https://www.amazon.com/s?i=specialty-aps&bbn=16225006011&rh=n%3A%2116225006011%2Cn%3A11058281&ref=nav_em__nav_desktop_sa_intl_makeup_0_2_11_2”
session <- bow(url,
               user_agent = "Student's Demo Educational")
session

session_page <- scrape(session)
div_elements <- html_nodes(session_page,'sg-col-20-of-24 s-matching-dir sg-col-16-of-20 sg-col sg-col-8-of-12 sg-col-12-of-16')

links <- character()
img_srcs <- character()
titles <- character()
prices <- character()
ratings <- character()

for (div_element in div_elements) {
  
  for (div_element in div_elements) {
  
  a_element <- html_node(div_element, '<a-link-normal celwidget" id="customer-reviews-content" aria-label="Top reviews" href="#")
  
 a-link-normal a-color-tertiary" href="/Beauty-Makeup-Skin-Hair-Products/b/ref=dp_bc_aui_C_1?ie=UTF8&amp;node=3760911">

```


#Amazon
```{r}
library(rvest)
library(polite)

url <- "https://www.amazon.com/s?i=specialty-aps&bbn=16225006011&rh=n%3A%2116225006011%2Cn%3A11058281&ref=nav_em__nav_desktop_sa_intl_makeup_0_2_11_2
"
session <- bow(url,
               user_agent = "Student's Demo Educational")
session
session_page <- scrape(session)

links <- character()
img_srcs <- character()
categories <- character()
products <- character()
price <- numeric()
description <- character()
ratings <- numeric()
reviews <- character()

<a id="customer-reviews-content" aria-label="Top reviews" class="a-link-normal celwidget" href="#" data-csa-c-id="imrjmp-44equr-z2bckm-9r0ofd" data-cel-widget="customer-reviews-content"></a>
```
